The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-29 manuscript/manuscript.Rnw
use bf instead of emph for keywords

These observations lead to two related questions: 1) what are the
genes which are responsible for the \emph{core functionality of the
  placenta} and 2) which genes are associated with \emph{changes in
  placenta morphology}?

>>>>

These observations lead to two related questions: 1) what are the
genes which are responsible for the \textbf{core functionality of the
  placenta} and 2) which genes are associated with \textbf{changes in
  placenta morphology}?
